---
title: "Fiscal Reporting"
output: pdf_document
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(tidyr)
library(readxl)
library(DT)
sbs <- read_excel("sbs_tef.xlsx")
```


**Before submitting make sure the name of your files contain both the quarter (eg. Q3) and the short code name for your campus. Search the table below to find your campus short code name.**

```{r, echo=FALSE, warning=FALSE, message=FALSE}
datatable(sbs, class = 'cell-border stripe', rownames = FALSE,
          options = list(pageLength = 5))
```

# Time and Effort

Use the uploader below to browse to and select your Time and Effort form. 

<script src="https://csuchico.app.box.com/upload-widget/embed.js?folderID=61817025515&height=420&isDescriptionFieldShown=0&isEmailRequired=1&title=Submit%20File(s)%20to%20Time_Effort&token=dyua1vg9v07hb5ek8dmis64au4x9g3bq&width=385" type="text/javascript"></script>

----

# Invoice and State Share Documentation

Use the uploader below to browse to and select your Invoice and State Share Documentation Report (SSDR)

<script src="https://csuchico.app.box.com/upload-widget/embed.js?folderID=61819231600&height=420&isDescriptionFieldShown=0&isEmailRequired=1&title=Submit%20File(s)%20to%20Invoice_SSDR&token=vq1x67481c88ryaes8o8ed9udwo90nha&width=385" type="text/javascript"></script>
